An exploratory analysis of the influence of resource use on the yield versus quality trade-off in Australian vineyards

### 2023-08-02 article.tex
Fixed error with figure references

\begin{figure}\label{fig:violin}

@@

  \caption{Violin plots of GI Region and Year coefficients for each model.}

@@

\begin{figure}\label{fig:yield_vs_value}

@@

  \caption{Scatter plot of vineyard yield against the product of yield and average price per tonne. The axes are in standard deviations with points coloured by climate.}

@@

\begin{figure}\label{fig:yield_vs_value_area}

@@

    \caption{Scatter plot of vineyard yield against the product of yield and average price per tonne as ratios to area harvested. The axes are in standard deviations with points coloured by climate.}

@@

\begin{figure}\label{fig:map}

@@

  \caption{Map of regional average yield and value per hectare.}

>>>>

\begin{figure}

@@

  \caption{Violin plots of GI Region and Year coefficients for each model.}\label{fig:violin}

@@

\begin{figure}

@@

  \caption{Scatter plot of vineyard yield against the product of yield and average price per tonne. The axes are in standard deviations with points coloured by climate.}\label{fig:yield_vs_value}

@@

\begin{figure}

@@

    \caption{Scatter plot of vineyard yield against the product of yield and average price per tonne as ratios to area harvested. The axes are in standard deviations with points coloured by climate.}\label{fig:yield_vs_value_area}

@@

\begin{figure}

@@

  \caption{Map of regional average yield and value per hectare.}\label{fig:map}
